\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{times}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

% Remove page numbers
\pagestyle{empty}

% Section formatting - simple and ATS-friendly
\titleformat{\section}
  {\large\bfseries\uppercase}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing*{\section}{0pt}{12pt}{6pt}

% Custom commands for consistent formatting
\newcommand{\resumeheader}[1]{\textbf{#1}}
\newcommand{\resumedate}[1]{#1}
\newcommand{\resumelocation}[1]{#1}

\begin{document}

% Header Section
\begin{center}
{\Huge\bfseries MUHAMMED SWALAHUDHEEN CV}\\[0.5em]
\href{mailto:cvsalahu12@gmail.com}{\underline{cvsalahu12@gmail.com}} \textbar\ \href{tel:+918590811546}{\underline{+91 8590811546}} \textbar\ \href{https://www.linkedin.com/in/salahu-cv-a98196230}{\underline{linkedIn/salahu-cv-a98196230}} \textbar\ \href{https://github.com/salahu01}{\underline{github/salahu01}}
\end{center}

\vspace{0.3em}

% Professional Experience
\section{Professional Experience}

\vspace{0.5em}

\noindent\href{https://www.fegno.com}{\underline{\textbf{Fegno Technologies LLP}}} \textbar\ \textbf{Software Development} \hfill \href{https://maps.app.goo.gl/7GvnNUNr6DXm98947}{\underline{Kakkand, Ernakulam}} \textbar\ \resumedate{Sep 2023 -- Present}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Single-handedly developed a comprehensive MDM (Mobile Device Management) POC within one week}, demonstrating expertise in core enterprise-level technology, which directly secured a multi-crore project for the company and showcased exceptional technical capability and rapid delivery.
    \item \textbf{Led cross-functional development teams}, driving collaboration and innovation while ensuring the timely delivery of high-quality applications that met and exceeded client expectations.
    \item \textbf{Successfully released and maintained multiple Flutter applications}, managing the entire lifecycle from concept to deployment, resulting in consistently high user engagement and satisfaction.
    \item \textbf{Architected and optimized CI/CD pipelines}, revolutionizing automation for build, test, and deployment processes, which led to faster release cycles and minimized manual errors.
    \item \textbf{Seamlessly integrated a range of third-party services and APIs}, expanding application capabilities and delivering enhanced user experiences through robust external connections.
\end{itemize}

\vspace{1em}

\noindent\href{https://www.sciwiz.net}{\underline{\textbf{SciWiz Technologies}}} \textbar\ \textbf{Software Development} \hfill \href{https://maps.app.goo.gl/J2GYANG4UUG6y44E7}{\underline{Vazhakkala, Ernakulam}} \textbar\ \resumedate{Jan 2022 -- Feb 2023}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Executed flawless pixel-perfect UI conversions} from intricate design mockups to fully functional Flutter applications, achieving superior visual fidelity and an exceptional user experience.
    \item \textbf{Engineered a comprehensive suite of testing strategies}, including unit, integration, and widget testing, to ensure reliable, high-quality code and deliver robust, bug-free applications.
    \item \textbf{Mentored and guided junior developers}, fostering a collaborative learning environment that accelerated skill development and improved overall team performance.
\end{itemize}

\vspace{1em}

\noindent\resumeheader{Freelancing} \textbar\ \textbf{Software Development} \hfill \resumedate{Jun 2021 -- Present}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Cultivated strong client relationships through clear and effective communication}, translating business needs into technical solutions and providing ongoing support to ensure project alignment and satisfaction.
    \item \textbf{Pioneered and contributed to high-impact open-source projects}, tackling complex business logic and technical challenges, while actively engaging with the Flutter community to drive innovation and collaboration.
    \item \textbf{Drove product vision and strategy}, aligning development efforts with business goals to create impactful applications that solved real-world problems and delighted users.
\end{itemize}

\vspace{0.2em}

% Projects
\section{Projects}

\vspace{0.5em}

\noindent{\textbf{MDM POC (Mobile Device Management)}} \hfill \textbf{Android, Java, Bazel, FCM, iOS, APNS, React, Supabase}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Delivered enterprise-grade MDM solution in one week}, demonstrating exceptional speed and technical capability that directly secured a multi-crore project for the organization.
    \item \textbf{Built cross-platform solution for Android and iOS} using native APIs, showcasing expertise in enterprise mobility and platform-specific development.
    \item \textbf{Implemented core MDM capabilities} including remote device enrollment, policy enforcement, application management, remote wipe, and compliance monitoring.
    \item \textbf{Proven ability to deliver high-impact results independently}, translating complex technical requirements into business value and revenue generation.
\end{itemize}

\vspace{2em}

\noindent\href{https://pub.dev/packages/feg_cli}{\underline{\textbf{Feg CLI}}} \hfill \textbf{Dart, Mason, Bricks}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Dramatically reduced development time and costs} by transforming week-long project creation processes into a single command, delivering significant time and cost savings for every Flutter project and enabling faster time-to-market.
    \item \textbf{Conceived and single-handedly developed an open-source CLI solution} that revolutionized Flutter project architecture at Fegno Technologies, establishing standardized architecture and best practices where none existed before.
    \item \textbf{Automated project scaffolding, repetitive tasks, and code generation} enabling consistent, scalable project structures across all Flutter applications and eliminating architectural inconsistencies.
    \item \textbf{Automated complex workflows} including API code generation from Postman collections, ready-built authentication solutions, token management, and API integration templates, eliminating manual repetitive work.
    \item \textbf{Delivered measurable business impact} through process optimization, demonstrating ability to identify inefficiencies and create innovative solutions that drive organizational productivity and cost reduction.
\end{itemize}

\vspace{0.5em}

\noindent{\textbf{Shopprix}} \hfill \textbf{Flutter, Bloc, Clean Architecture, Python, Postgress, Redis}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Developed an eCommerce application} for Fegno Technologies, focusing on creating a scalable, maintainable codebase with a strong separation of concerns, ensuring a robust and efficient shopping experience for users.
\end{itemize}

\vspace{0.5em}

\noindent\href{https://www.majarat.ae/}{\underline{\textbf{Majarat}}} \hfill \textbf{Flutter, MVC architecture, Getx}\\[-0.6em]
\begin{itemize}[leftmargin=*,itemsep=0.1em,topsep=0em]
    \item \textbf{Developed an eCommerce application as a freelancing project} using the MVC architecture and GetX state management, creating a seamless and intuitive shopping experience, optimizing performance, and ensuring robust state management throughout the app.
\end{itemize}

\vspace{0.5em}

% Education
\section{Education}

\resumeheader{Bachelor of Computer Application} \hfill \resumedate{Present}\\
\textbf{Lovely Professional University} \hfill \resumelocation{Punjab}

\vspace{0.2em}

% Skills
\section{Skills}

\textbf{Languages:} Dart, Kotlin, Java, Swift, Java Script, Type Script, Ruby, Bash, C++, C, SQL\\
\textbf{Technology:} Flutter, Node, Git, AWS, Docker, Fastlane, Codemagic, Firebase, MongoDB, GraphQL, Selenium, Webdriver IO\\
\textbf{Flutter Development:} State Managements, CI/CD, Automations, IOT

\end{document}

